---
output: github_document
bibliography: inst/ref.bib
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# usdai

<!-- badges: start -->
<!-- badges: end -->

Typical asymptotic theory for hypothesis testing requires that our dimension $d$ remain constant as the sample size $n$ grows. `usdai` provides methods for conducting hypothesis tests about the mean and variance of high-dimension datasets in absence of this assumption, requiring no prior knowledge of the behavior of $d$ as $n$ goes to infinity.

This testing procedure is based on the self-normalized cross U-statistic--- see @wang2020hypothesis and @shao2015self for descriptions of the self-normalization process and  @kim2024dimension for description of the cross U-statistic--- whose asymptotic density is plotted in @lobato2001testing.

## Installation

You can install the development version of usdai from [GitHub](https://github.com/) with:

``` {r, eval=FALSE}
# install.packages("devtools")
devtools::install_github("wchalstead/usdai")
```

## Example

The usdai gives methods for dimension agnostic hypothesis testing.
```{r example}
library(usdai)
```

Consider a situation in which we have $100$ realizations of a multivariate normal vector in $\mathbb{R}^{10}$, and we want to test whether $\mu = 0$. This is equivalent to testing that the $\ell_4$ norm of the vector $\mu$ is zero.

We can perform such a test as follows:

First, we generate data with true mean $\mu = 0$
```{r}
set.seed(1232)
# Generate Data
data <- matrix(rnorm(200 * 10), 200, 10)
```

And we can use the `crossWStatL4` function to get a test statistic, and a p-value can be recovered using the `pcrossW` which approximates the CDF of the asymptotic distribution.
```{r}
W.test <- crossWStatL4(data, 100)
pval <- 1 - pcrossW(W.test)
paste(pval)
```
With a large p-value as above, we fail to reject the null hypothesis that $\mu = 0$.

Now consider a situation with true mean $\mu = 0.2$
```{r}
set.seed(1213)
# Generate Data
data <- matrix(rnorm(200 * 10, mean = 0.2), 200, 10)
```

And we can use the `crossWStatL4` function to get a test statistic, and a p-value can be recovered using the `pcrossW` which approximates the CDF of the asymptotic distribution.
```{r}
W.test <- crossWStatL4(data, 100)
pval <- 1 - pcrossW(W.test)
paste(pval)
```
With the small p-value as above, we reject the null hypothesis $\mu = 0$.

Beyond this mean testing example above, the usdai package also includes functions such as `crossWStatL4` that allow for variance testing as well. Additionally, the functions `qcrossW`, `pcrossW`, `rcrossW`, and `dcrossW` allow for quantile, distribution and random generation of the asymptotic testing distribution.

## References
