---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# usdai

<!-- badges: start -->
<!-- badges: end -->

Typical asymptotic theory for hypothesis testing requires that our dimension $d$ remains constant as the sample size $n$ grows. `usdai` provides methods for conducting hypothesis tests about the mean and variance of high-dimension datasets in absence of this assumption, requiring no prior knowledge of the behavior of $d$ as $n$ goes to infinity.

## Installation

You can install the development version of usdai from [GitHub](https://github.com/) with:

``` {r, eval=FALSE}
# install.packages("devtools")
devtools::install_github("wchalstead/usdai")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(usdai)
## basic example code
```
