---
output: github_document
bibliography: inst/ref.bib
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# usdai

<!-- badges: start -->
<!-- badges: end -->

Typical asymptotic theory for hypothesis testing requires that our dimension $d$ remain constant as the sample size $n$ grows. `usdai` provides methods for conducting hypothesis tests about the mean and variance of high-dimension datasets in absence of this assumption, requiring no prior knowledge of the behavior of $d$ as $n$ goes to infinity.

This testing procedure is based on the self-normalized cross U-statistic--- see @wang2020hypothesis and @shao2015self for descriptions of the self-normalization process and  @kim2024dimension for description of the cross U-statistic--- whose asymptotic density is plotted in @lobato2001testing.

## Installation

You can install the development version of usdai from [GitHub](https://github.com/) with:

``` {r, eval=FALSE}
# install.packages("devtools")
devtools::install_github("wchalstead/usdai")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(usdai)
## basic example code
set.seed(12)
# Generate Data
data <- matrix(rnorm(100 * 2), 100, 2)
# Calculate U-Statistic
crossUStatL4(data, 50)
```

## To-Do
I would like to move my current code to C++ to improve the computation time while implementing basic tests to make sure that my computations are still correct as I transfer my code over. Another priority is finishing all of the documentation for my exported functions. A final thing that I would like to add is a function to simulate random variables from the asymptotic distribution, but I will likely need to do some testing to decide if it is more efficient to try and generate these by generating a uniform random variable on (0, 1) and passing this as a function to some pre-computed set of quantiles or finding a way to efficiently integrate over a random process.

## References
